\documentclass{article}

\begin{document}

\section{Birdwatching}

Write a script in Prolog able to determine which bird is the one you're looking at given the following information about its taxonomy:

If the family is albatross and the color is white, then the bird is the laysan albatross.
Another bird of the same family is the black footed albatross, however its color is dark.
If the voice (or call) of the bird is a muffled musical whistle and belongs to the swan family, then the bird is a whistling swan.
However, noisier swans (like the trumpeter swan) exist on the same family, which voices resemble loud trumpeting.
If its nostrils are external tubes, the bird lives at sea, and its bill is hooked, then it belongs to the tubenose order.
It's easy to identify members of the waterfowl order if their feet are webbed and their bill is flat.
If a bird of the tubenose order, is considered large, and its wings are long, then it belongs to the albatross family.
If its neck is long, the color is white, its flight is ponderous and the bird belongs to the waterfowl order, then it also belongs to the swan family.

The bird you're looking at has external tubes as nostrils, lives at sea, has a hooked bill, is considered large, has long wings and is dark-colored.

You may need the \texttt{discontiguous/1} predicate at the top of your script, which receives a list of predicate \textit{signatures} (that is, \texttt{predicate/\#arguments}) of those predicates which can't be inferred from your source code. In other words, those predicates ``not used'' in your file, e.g. information about other birds which are not being observed.

\pagebreak

\section{The Spaceship}

The crew of a derelict spaceship is asleep in the cryo-chambers.
In the meantime, the MUL-T robot unit is preparing the uniforms and tools prior to landing, but a complete description of whom uses which tool is not provided. Instead, there are pieces of information scattered through the ship. The information reads:

\begin{itemize}
    \item The Commando has a shotgun.
    \item The Engineer wears purple while the Loader prefers yellow.
    \item The Mercenary has a blue suit.
    \item Someone uses a white robe and a Kyaro's ring.
    \item The Huntress wears red and has a bow.
    \item The crew member with orange clothing holds a shotgun.
    \item Two tactical turrets are the tools of the crew member who wears purple.
    \item The katana belongs to the crew member in blue.
    \item The Artificer uses a Kyaro's ring.
    \item The crew member with a yellow vest uses a reinforced armor.
\end{itemize}

Write a program in prolog to generate a full description of the uniforms and tools of all six crew members.

\end{document}